Stats

### 2022-04-28 stats/analysis.Rmd
new fig4, fix ccAge calculation error, incorporate some of M feedback

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(viridis) # col scales, plotting...
library(ggpubr)
library(ggridges)
library(ggthemes)
library(tidyboot) # for bootstrap CIs
library(brms) # modeling
library(splithalfr) # reliability

@@

```{r extvali_plot}
extvaliPostSamples <- bind_rows(
  posterior_samples(mExtvaliccAge, pars = "b_ccAge") %>% mutate(model = "mExtvaliccAge") %>% rename(estimate = b_ccAge), 
  posterior_samples(mExtvaliccHours, pars = "b_ccHours") %>% mutate(model = "mExtvaliccHours") %>% rename(estimate = b_ccHours), 
  posterior_samples(mExtvalihhTotal, pars = "b_hhTotal") %>% mutate(model = "mExtvalihhTotal") %>% rename(estimate = b_hhTotal), 
  posterior_samples(mExtvalihhSibs, pars = "b_hhSibs") %>% mutate(model = "mExtvalihhSibs") %>% rename(estimate = b_hhSibs),
  posterior_samples(mExtvalisibsChildAged, pars = "b_sibsChildAged") %>% mutate(model = "mExtvalisibsChildAged") %>% rename(estimate = b_sibsChildAged),
  posterior_samples(mExtvalisiblingsVarietyScoreP, pars = "b_siblingsVarietyScoreP") %>% mutate(model = "mExtvalisiblingsVarietyScoreP") %>% rename(estimate = b_siblingsVarietyScoreP),
  posterior_samples(mExtvalisiblingsVarietyScoreW, pars = "b_siblingsVarietyScoreW") %>% mutate(model = "mExtvalisiblingsVarietyScoreW") %>% rename(estimate = b_siblingsVarietyScoreW),
  posterior_samples(mExtvaliPE, pars = "b_pe") %>% mutate(model = "mExtvaliPE") %>% rename(estimate = b_pe)
) %>% 
  mutate(
    model = factor(model, levels = extvaliModelorder, labels = c("sibling variety score (Cassidy et al., 2005)", "number of children in household aged 1-12", "number of children in household aged 0-18", "null model", "number of household members", "average hours spent in childcare per day", "age of childcare entry", "sibling variety score (Peterson, 2000)", "peer exposure index"))  
  )

write.csv(extvaliPostSamples, "../saves/extvali-posteriorsamples.csv", quote = F, row.names = F)
saveRDS(extvaliPostSamples, "../saves/extvali-posteriorsamples.rds")

ggplot(extvaliPostSamples, aes(x = estimate, y = model, fill = factor(stat(quantile)))) +
  geom_vline(xintercept = 0, lty = 2, alpha = .75) +
  stat_density_ridges(
    geom = "density_ridges_gradient",
    calc_ecdf = TRUE, 
    quantiles = c(0.025, 0.975)
  ) +	
  scale_fill_manual(values = c("firebrick", "NA", "firebrick"), guide = "none") + 
  scale_x_continuous(limits = c(-0.25, 0.75)) + 
  ylab("")

ggsave("../figures/extvali-posteriorsample.png", width = 6, height = 3)
```

@@

>>>>

```{r load_packages, message=FALSE, warning=FALSE, include=FALSE}
library(tidyverse) # data handling etc.
library(viridis) # col scales, plotting...
library(ggpubr)
library(ggridges)
library(ggthemes)
library(tidyboot) # for bootstrap CIs
library(brms) # modeling
library(splithalfr) # reliability 
library(tidybayes) # for stat_halfeye
library(ggdist)

@@

@@

```{r extvali_posteriordraws}
extvali_draws <- bind_rows(
  mExtvaliccAge %>% gather_draws(b_ccAge),
  mExtvaliccHours %>% gather_draws(b_ccHours), 
  mExtvalihhTotal %>% gather_draws(b_hhTotal), 
  mExtvalihhSibs %>% gather_draws(b_hhSibs), 
  mExtvalisibsChildAged %>% gather_draws(b_sibsChildAged), 
  mExtvalisiblingsVarietyScoreP %>% gather_draws(b_siblingsVarietyScoreP), 
  mExtvalisiblingsVarietyScoreW %>% gather_draws(b_siblingsVarietyScoreW),
  mExtvaliPE %>% gather_draws(b_pe)
  ) %>% 
  mutate(
    Predictor = factor(.variable, 
                       levels = c("b_hhSibs", 
                                  "b_siblingsVarietyScoreP", 
                                  "b_sibsChildAged", 
                                  "b_hhTotal", 
                                  "b_ccHours", 
                                  "b_ccAge", 
                                  "b_siblingsVarietyScoreW", 
                                  "b_pe"), 
                       labels = c("Number of children in household aged 0-18", 
                                  "Sibling variety score (Peterson, 2000)", 
                                  "Number of children in household aged 1-12", 
                                  "Number of household members", 
                                  "Average hours spent in childcare per day", 
                                  "Age of childcare entry", 
                                  "Sibling variety score (Cassidy et al., 2005)", 
                                  "Peer exposure index")
                       )  
  )

write.csv(extvali_draws, "../saves/extvali-draws.csv", quote = F, row.names = F)
saveRDS(extvali_draws, "../saves/extvali-draws.rds")
```

```{r extvali_plot}
ggplot(extvali_draws, aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 tidybayes::stat_halfeye(alpha = .7, .width = c(.95, .80), scale = 3) +
    labs(x = "Posterior estimate", y = "")+
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00")) +
  xlim(-0.2, 0.6) +
  theme_minimal()

extvali_draws %>% 
  filter(
          Predictor == "Peer exposure index" ||
          Predictor == "Sibling variety score (Cassidy et al., 2005)" ||
          Predictor == "Number of children in household aged 0-18" ||
          Predictor == "Average hours spent in childcare per day", 
         ) %>% 
  ggplot(., aes(y = Predictor, x = .value, fill = stat(x) > 0)) +
 tidybayes::stat_halfeye(alpha = .8, .width = c(.95, .80)) +
    labs(x = "Posterior estimate", y = "") +
  guides(fill = "none")+
  geom_vline(xintercept = 0, linetype = "dashed") +
  scale_fill_manual(values = c("grey","#85AD00")) +
  scale_x_continuous(limits = c(-0.6, 1), breaks = seq(-0.5, 1, 0.25)) + 
  theme_minimal()

ggsave("../figures/extvali_results.png", width = 10, height = 6, scale = 0.7, bg = "white")
```
